%
%  RAL XFEL FEE CCC/ASIC interface manual
%
%  Created by Sam Cook on Mon 28 Jan 2013
%
%  Copyright (c) 2013 RAL. All rights reserved.
%
\documentclass[12pt]{book}

% Use utf-8 encoding for foreign characters
\usepackage[utf8]{inputenc}

% Setup for fullpage use
\usepackage{fullpage}

% Uncomment some of the following if you use the features
%
% Running Headers and footers
%\usepackage{fancyhdr}

% Multipart figures
\usepackage{subcaption}

% Multirow tables
\usepackage{multirow}

% More symbols
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{wasysym}
\usepackage{latexsym}

% Surround parts of graphics with box
% \usepackage{boxedminipage}

% Stop the float madness! doesn't seem to work, stick with htbp
% \usepackage{float} 

% Package for including code in the document
\usepackage{listings}

% Package for including code in the document
\usepackage{minted}
% If you want to generate a toc for each chapter (use with book)
\usepackage{minitoc}

% This is now the recommended way for checking for PDFLaTeX:
\usepackage{ifpdf}

% Add a bit of extra height to tables so '\hlines' don't look crap
\usepackage{array}
\setlength{\extrarowheight}{1.5pt}
% Specify a new column type 'X' that is fixed width and centred
% \newcolumntype{X}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt} } p{#1} }
\newcolumntype{X}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
% This gives better decimel place alignment (apparently)
% Still needs multicolumns in the header to align correctly
\usepackage{dcolumn}
% Arguments are:
% D<column sep (instead of &)><column sep to insert><n decimal places>
\newcolumntype{d}[1]{D{.}{.}{#1}}

% Set footnotes to be symbols as it stops random powers appearing
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
% Reset the footnote 'counter' every page
\usepackage{perpage} %the perpage package
\MakePerPage{footnote} %the perpage package command

% Create tables of a defined total width with wrapped columns
\usepackage{tabulary}
% threeparttable gives us access to footnotes in tables
\usepackage{threeparttable}
% wan to get ditto mark
\usepackage[T1]{fontenc}
\newcommand*{\dittostraight}{---\textquotedbl---} % available in T1 encoding

% We want a nice tick & cross symbol for comparison tables
\usepackage{pifont} 
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\mus}{$~\mu$s}

% make bullet point lists with tighter spacing
\usepackage{mdwlist}
%\newif\ifpdf
%\ifx\pdfoutput\undefined
%\pdffalse % we are not running PDFLaTeX
%\else
%\pdfoutput=1 % we are running PDFLaTeX
%\pdftrue
%\fi

% rotating also includes graphicx so don't double import (causes error)
\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi

% Allow full page landscape images
\usepackage{rotating}

\usepackage{titling}

\usepackage{fixltx2e}

% lineup from jpconf
\def\lineup{\def\0{\hbox{\phantom{0}}}%
    \def\.{\hbox{$\phantom{.}$}}%
    \def\m{\hbox{$\phantom{-}$}}%
    \def\-{\llap{$-$}}}

\title{Characterisation of the MuSIC muon beam and design of the Eu-XFEL LPD/CCC interface firmware}
\author{Samuel Leslie Cook}

\graphicspath{{4_appendix_XFEL/}{1_introduction/}{3_measurements/}{2_simulation/}}
\renewcommand{\sfdefault}{phv}
\begin{document}    

    % \maketitle
    \begin{titlepage}
      \begin{center}
        \vspace*{3cm}
        
        \huge
        \textbf{\thetitle}

        \vspace{2cm}

        \textbf{\theauthor}

        \vfill
        \large
        UCL\\
        \vspace{0.8cm}
        High Energy Physics\\
        \vspace{0.8cm}
        Submitted to UCL in fulfilment of the requirements for the award of the degree of PhD.

      \end{center}
    \end{titlepage}
    
    \chapter*{Declaration} % (fold)
      I, \theauthor, confirm that the work presented in this thesis is my own.
      Where information has been derived from other sources, I confirm that
      this has been indicated in the thesis.
      \vspace*{3cm}
      \begin{flushright}
      \theauthor\hspace*{0.1\textwidth}\rule{0.5\textwidth}{0.25pt}
      \end{flushright}
    % chapter  (end)
    
    \chapter*{Abstract} % (fold)
      As it is now known that neutrinos oscillate, this entails that lepton number is not a conserved quantity and required modification of the Standard Model.  The same mechanism also allows charged leptons to violate lepton number, but at an immeasurable rate.  Therefore any observation of e.g. a muon decaying to an electron in the absence of neutrinos would be a signal of physics beyond the Standard Model.  A test facility, but also an experiment capable of searching for such a kinematic effect has been set-up in Osaka, Japan.

      The thesis `Initial Measurements at the MuSIC Beam-Line' documents several experiments that were carried out using the MuSIC muon beam in Osaka. The experiments focused on understanding the beam and characterising it. Three main measurements were made: total charged particle flux, muon flux and muon momentum spectrum. 

      Each experiment used plastic scintillators and MPPCs to detect the charged particles. Muons were identified by looking for muon decays between two scintillators. Data acquisition was performed using NIM for signal shaping and logic; and CAMAC or VME for readout via TDC and ADC modules. 

      In addition to direct experimental measurements, a simulation of MuSIC was made using the `G4Beamline' and `Geant4' packages which allowed detailed interrogation of the experiment to aid understanding of the results.  It also provided a test bed upon which to refine the setup for later measurements. 

      These measurements allow us to confirm the performance of the novel pion capture solenoid which is an integral part of several future experiments (primarily COMET but also proposed neutrino factories).

      In addition to this core work, the thesis deals with my services writing firmware for the LPD detector being built for the XFEL project in Hamburg, Germany. The firmware is an interface between the generic clock and control card (being developed at UCL) and the custom ASIC (being developed at RAL). The interface was written using VHDL and receives, translates, interprets then transmits control instructions to the detector.
    
    % chapter abstract (end)
    
    %% ToC
    \tableofcontents

    %%% Technically UCL want these here - let's see if they care
    \listoffigures
    \listoftables
    
    \include{1_introduction/Content}
    \include{2_simulation/Content}
    \include{3_measurements/Content}
    \include{4_appendix_XFEL/appendix_xfel_intro}
    \include{4_appendix_XFEL/Content}
    
    \bibliographystyle{h-elsevier}
    \bibliography{thesis_bib}
\end{document}
    
% 